R Notebook

### 2021-06-22 Exemples and Implementations.Rmd
Tutto funzionante

  vpar        = var(pars)
  ms          = a*pars+(1-a)*matrix(mpar,N,3,byrow=T)
  mus         = pars[,1]+pars[,2]*xs 
  weight      = w*dnorm(y[1],0,exp(mus/2))
  k           = sample(1:N,size=N,replace=T,prob=weight)
  ms1         = ms[k,] + matrix(rnorm(3*N),N,3)%*%chol(h2*vpar)
  xt          = rnorm(N,ms1[,1]+ms1[,2]*xs[k],exp(ms1[,3]/2))
  w           = dnorm(data[t],0,exp(xt/2))/dnorm(data[t],0,exp(mus[k]/2))
  w           = w/sum(w)
  ESS         = 1/sum(w^2)

@@

```{r include=FALSE}
set.seed(12345)
N=5000
svpf<-SVPFfun(y,N,m0,C0,alpha,beta,tau)
svapf<-SVAPFfun(y,N,m0,C0,alpha,beta,tau)
set.seed(1235)
svlw<-SVLWfun(y,N=1000,m0,C0,ealpha=0.12,valpha=0.4,ebeta=1,vbeta=0.3,nu=0.11,lambda=0.1)
```

>>>>

  vpar        = var(pars)
  ms          = a*pars+(1-a)*matrix(mpar,N,3,byrow=T)
  mus         = pars[,1]+pars[,2]*xs 
  weight      = w*dnorm(data[t],0,exp(mus/2))
  k           = sample(1:N,size=N,replace=T,prob=weight)
  ms1         = ms[k,] + matrix(rnorm(3*N),N,3)%*%chol(h2*vpar)
  xt          = rnorm(N,ms1[,1]+ms1[,2]*xs[k],exp(ms1[,3]/2))
  w           = dnorm(data[t],0,exp(xt/2))/dnorm(data[t],0,exp(mus[k]/2))
  w           = w/sum(w)
  ESS         = 1/sum(w^2)

@@

```{r include=FALSE}
set.seed(12345)
N=5000
svpf<-SVPFfun(y,N,m0,C0,alpha,beta,tau)
svapf<-SVAPFfun(y,N,m0,C0,alpha,beta,tau)
svlw<-SVLWfun(y,N,m0,C0,ealpha,valpha,ebeta,vbeta,nu,lambda)
```
